High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2020-10-30 paper/main.tex
working through reviewer 3 concerns [WIP]

@@

We validated our approach using synthetic data where the underlying
correlations were known.  We then applied our framework to a
neuroimaging dataset collected as participants listened to either an
audio recording of a ten-minute story, listened to a temporally scrambled
version of the story, or underwent a resting state
scan~\citep{SimoEtal16}.  We used a subset of the data to train
across-participant classifiers to decode listening times using a blend
of neural features (comprising neural activity patterns, as well as
different orders of dynamic correlations between those patterns that
were inferred using our computational framework).  We found that both
the PCA-based and eigenvector centrality-based approaches yielded
neural patterns that could be used to decode accurately (i.e., well above
chance).  Both approaches also yielded the best decoding accuracy for
data collected during (intact) story listening when high-order (PCA:
second-order; eigenvector centrality: fourth-order) dynamic
correlation patterns were included as features.  When we trained
classifiers on the scrambled stories or resting state data, only
lower-order dynamic patterns were informative to the decoders.  Taken
together, our results indicate that high-level cognition is supported
by high-order dynamic patterns of communication between brain
structures.

>>>>

One reason one might expect to see homologous networks in a dataset is
related to the notion that network dynamics reflect ongoing neural
computations or cognitive processing~\citep[e.g.,][]{BeatEtal16}.  If
the nodes in two brain networks are interacting (within each network)
in similar ways then, according to our characterization of network
dynamics, we refer to the similarities between those patterns of
interaction as higher-order correlations.  When higher-order
correlations are themselves changing over time, we can also attempt to
capture and characterize those high-order dynamics.

@@

We validated our approach using synthetic data where the underlying
correlations were known.  We then applied our framework to a
neuroimaging dataset collected as participants listened to either an
audio recording of a ten-minute story, listened to a temporally
scrambled version of the story, or underwent a resting state
scan~\citep{SimoEtal16}.  Temporal scrambling has been used in a
growing number of studies, largely by Uri Hasson's group, to identify
brain regions that are sensitive to higher-order and longer-timescale
information (e.g., cross-sensory integration, rich narrative meaning,
complex situations, etc.) versus regions that are primarily sensitive
to low-order (e.g., sensory) information.  For example,
\cite{HassEtal08} argues that when brain areas are sensitive to fine
versus coarse temporal scrambling, this indicates that they are
``higher order'' in the sense that they process contextual information
pertaining to further-away timescales.  By contrast, low-level
regions, such as primary sensory cortices, do not meaningfully change
their responses (after correcting for presentation order) even when
the stimulus is scrambled at fine timescales.

We used a subset of the story listening and rest data to train
across-participant classifiers to decode listening times using a blend
of neural features (comprising neural activity patterns, as well as
different orders of dynamic correlations between those patterns that
were inferred using our computational framework).  We found that both
the PCA-based and eigenvector centrality-based approaches yielded
neural patterns that could be used to decode accurately (i.e., well
above chance).  Both approaches also yielded the best decoding
accuracy for data collected during (intact) story listening when
high-order (PCA: second-order; eigenvector centrality: fourth-order)
dynamic correlation patterns were included as features.  When we
trained classifiers on the scrambled stories or resting state data,
only lower-order dynamic patterns were informative to the decoders.
Taken together, our results indicate that high-level cognition is
supported by high-order dynamic patterns of communication between
brain structures.
